Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-22 NEUROC/sec3-experiment-design.tex
更新了Hyper-parameters中的表述

% added by wangyupan, 2020-12-21 ----start----
In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
%
That was, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}. 
%
We trained for a maximum of 100k epochs. 
%
If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
%
We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
%
Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
% added by wangyupan, 2020-12-21 ----end----

>>>>

% added by wangyupan, 2020-12-21 ----start----
We used Adam \cite{diederik2015_adam} with a learning rate of 0.01 and a weight decay of 1e-5.
%
We initialized weights using initialization described in \cite{xavier2010_glorot} and initialized bias with zeros.
%
In the accuracy experiment of hyper-parameters, we trained all models for a maximum of 10k epochs and used early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
We stopped training if the validation loss did not improve for 50 epochs. We reported the test accuracy of the epoch with the lowest validation loss.
% added by wangyupan, 2020-12-21 ----end----
